A convenient, flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate

### 2022-06-08 src/tex/ms.tex
[showyourwork] overleaf sync

Since the delay time of BBHs can range from Myrs to multiple Gyrs, the birth environment of BBHs varies significantly and we cannot ignore the cosmological (metallicity) evolution of the Universe. 
The rate of Binary Black Hole (BBH) mergers at different redshifts depends both on the delay time distribution as well as the metallicity dependent star-formation rate density (\SFRDzZ).
The assumed cosmic star formation rate density (SFRD) will therefore greatly influence the observed rate of double compact object mergers \citep{Neijssel+2019, Chruslinska2019, Boco2020,Broekgaarden+2021a}. 
Moreover, it is the nuclear reactions in massive stars are responsible for the metal enrichment of the Universe at high redshift. The birth of massive stars, and their death as BHs are thus inseparable from the evolution of the metallicity distribution of the Universe.

@@

To construct \SFRDzZ from empirical data, one can estimate \dpdZ by combining observed mass-metallicity relations with galaxy stellar mass functions \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019, Broekgaarden+2021b}. Alternatively, one could extract \SFRDzZ directly from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.

@@

In Figure \ref{fig: fit SFRD} we show the shape of this \SFRDzZ in the plane of the

>>>>

Since the delay time of BBHs can range from Myrs to multiple Gyrs, the birth environment of BBHs varies significantly and we cannot ignore the cosmological (metallicity) evolution of the Universe. 
The rate of Binary Black Hole (BBH) mergers at different redshifts depends both on the delay time distribution as well as the metallicity dependent star-formation rate density (\SFRDzZ).
The assumed cosmic star formation rate density (SFRD) will therefore greatly influence the observed rate of double compact object mergers \citep{Neijssel+2019, Chruslinska2019_obs, Boco2020,Broekgaarden+2021a}. 
Moreover, it is the nuclear reactions in massive stars are responsible for the metal enrichment of the Universe at high redshift. The birth of massive stars, and their death as BHs are thus inseparable from the evolution of the metallicity distribution of the Universe.

@@

To construct \SFRDzZ from empirical data, one can estimate \dpdZ by combining observed mass-metallicity relations with galaxy stellar mass functions \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_obs, Broekgaarden+2021b}. Alternatively, one could extract \SFRDzZ directly from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.

@@

In Figure \ref{fig: fit SFRD} we show the shape of this \SFRDzZ for different redshifts and metallicities. 
In the top panel we
